Supplemental Materials for ``Universals of word order reflect optimization of grammars for efficient communication''

### 2019-10-14 writeup/pnas-word-order-si.tex
code

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../results/plane/pareto-plane-perLanguage.pdf}
	\caption[Predictability and Parseability]{Predictability and parseability of 51 languages. Green: random baselines, Red: real grammar, blue: approximate Pareto frontier, computed from the optimized grammars.\footnotemark All data are $z$-scored. Languages are ordered by corpus size, measured by the number of sentences in the training partition, from largest (Czech) to smallest (Irish).}\label{fig:pareto-per-lang}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../results/plane/unlexicalized/pareto-plane-perLanguage-lexicalized-mle.pdf}
	\caption[Predictability and Parseability]{Study 1, replication with lexicalized models: Predictability and parseability of 51 languages, for \emph{lexicalized} models, compare Figure~\ref{fig:pareto-per-lang}.}\label{fig:pareto-plane-noPOS}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../results/plane/pareto-plane-perLanguage_withReal.pdf}
	\caption[Predictability and Parseability]{Predictability and parseability of 51 languages. Green: random baselines, Red: real grammar, blue: approximate Pareto frontier, computed from the optimized grammars.\footnotemark All data are $z$-scored. Languages are ordered by corpus size, measured by the number of sentences in the training partition, from largest (Czech) to smallest (Irish).}\label{fig:pareto-per-lang}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../results/plane/unlexicalized/pareto-plane-perLanguage-lexicalized-real.pdf}
	\caption[Predictability and Parseability]{Study 1, replication with lexicalized models: Predictability and parseability of 51 languages, for \emph{lexicalized} models, compare Figure~\ref{fig:pareto-per-lang}.}\label{fig:pareto-plane-noPOS}
\end{figure}
